
%________________________________________________________________________________________
% @brief    LaTeX Resume for Carl Myers
% @author   Carl Harris Myers
% @url      https://www.cmyers.org
% @date     March 20, 2016
% @info     based on info from http://www.maxburstein.com/blog/creating-resume-using-latex/
%________________________________________________________________________________________
\documentclass[line, margin]{res}

% from http://tex.stackexchange.com/questions/52351/quote-marks-are-backwards-using-texmaker-pdflatex
% \usepackage[english]{babel}
% \usepackage[autostyle]{csquotes}

\begin{document}
\name{\Large Carl Harris Myers}
\address{ Union City, CA $\bullet$ (206) 931-9916 $\bullet$ cmyers@cmyers.org $\bullet$ https://cmyers.org }

\begin{resume}

\section{OBJECTIVE}
As a senior software engineer with extensive internal tools experience, I want
to act as a force multiplier by creating and improving development ecosystems
that delight other developers.  I want this sphere of influence to extend to
the open source community.

\section{EXPERIENCE}
{\bf PernixData, Inc.} -- San Jose, CA
\\
\textit{Tools Engineer} \hfill {\bf June 2015 -- Present}
\\
\begin{itemize}
\item
Drove the migration from a legacy Git server to Atlassian Bitbucket Server.
Performed initial setup, data import, installation, and plugin configuration
for the new system.  Developed custom plugins to replace functionality of the
old system.  The new system delivered self-service features to 100+ developers
reducing the support burden.
\item
Wrote and maintained several additional plugins for the Atlassian ecosystem.
Delivered streamlined support by enabling self-service access to the
``unbreakable build system'' for all projects in the company.  See Github, source
available.
\item
Maintained legacy build systems while architecting new build tools to achieve
long-range company wide impact, with a focus on reliability, reproducibility,
transparency, and technology agnosticism.
\end{itemize}

{\bf Palantir Technologies, Inc.} -- Palo Alto, CA
\\
\textit{Software Engineer, Internal Tools Team} \hfill {\bf April 2009 -- June 2015}
\\
\begin{itemize}
\item
Drove the migration of source control from Subversion to Git.  Delivered an
``unbreakable build system'' which used Git to enable automated testing of code
before merge.  Palantir realized significant gains in productivity and quality.
\item
Wrote and maintained several plugins for the Atlassian ecosystem.  Delivered
reduced support burden by enabling self-service access to the ``unbreakable
build system'' for all projects in the company.  See Github, source available.
By 2015, over 500 projects were building using Stashbot, one such example.
\item
As the first and most tenured engineer on the ITOOLS team, provided scaled
support through guidance, best practices, customized tools, just-in-time
solutions, and proactive recommendations that decreased the support burden and
facilitated the exponential expansion of the company as they grew from 200 to
over 1000 employees.
\item
Evaluated newly-sourced talent through on-site and phone interviews to directly
contribute to the growth and success of the ITOOLS team.  I directly
contributed to the hire of every new employee on the ITOOLS team and performed
over 200 interviews.
\end{itemize}

{\bf Amazon.com} -- Seattle, WA
\\
\textit{SDE, Developer Applications Team} \hfill {\bf January, 2008 -- January, 2009}
\\
\begin{itemize}
\item
As lead engineer on a four person team, improved turn around times and reduced
translation costs by implementing an internal web service that provided string
translation and localization services.
\item
Evaluated newly-sourced talent through on-site and phone interviews.
\end{itemize}

\textit{Software Design Engineer, Developer Tools Team} \hfill {\bf March 2006 -- January, 2008}
\\
\begin{itemize}
\item
Maintained and supported a complex build system used by over 2000 developers
which focused on reproducibility, consistency, and dependency management of
large codebases.  Worked on a codebase which exceeded 200GB and 8 million
files, which was divided into more than 13,000 discrete packages.
\item
As primary owner of the source control repository, migrated to new hardware,
upgraded software, and ensured backups were functioning while responsible for a
priceless codebase containing over 8,000 engineer-years of work.
\item
Designed and implemented a distributed application which allowed internal
customers to view logs for the build system to assist in debugging.
\item
Performed porting and developed porting tools to assist in the migration from
Redhat 7.2 to Red Hat Enterprise Linux 3 and later to Red Hat Enterprise Linux
5 64-bit, saving the company over 20 million dollars during Q4 scaling alone.
\item
As part of the Environment Improvement Ninjas, used personal time to work on
porting the environment to new platforms, writing scripts to get metadata more
easily, and added tab completions, boosting productivity for myself and other
developers.  The Environment Improvement tools are used by almost every
developer at Amazon.
\item
Recruited and interviewed candidates both on-site and through phone screens,
and attended college recruiting events.
\end{itemize}

\section{EDUCATION}

{\bf Purdue University}, Lafayette, IN
\begin{itemize}
\item
Graduated in December of 2005 with a Bachelors in Electrical and Computer
Engineering.
\item
Coursework included Operating Systems Engineering, Advanced Object Oriented
Programming and Scripting, Object Oriented Design, Networking, Microprocessor
Architecture.
\end{itemize}

% Programming Expertise
\section{PROGRAMMING EXPERTISE}
\begin{itemize}
\item 
Java: 9 / 10, 10 years experience
\item 
Ruby: 7 / 10, 4 years experience
\item
Perl: 5 / 10, 3 years experience
\item
C++: 5 / 10, 3 years experience
\item
Python: 3 / 10, 1 year experience
\item
Also fluent with Bash/Zsh, SQL, Gradle, Maven, Make, Git, Debian/Ubuntu Linux, Centos/Redhat Linux
\end{itemize}

\section{OPEN SOURCE WORK}
{\bf Atlassian Bitbucket Server Plugin: Stashbot} \hfill Primary Author
\\
https://github.com/terabyte/stashbot
\\
{\bf Atlassian Bitbucket Server Plugin: Codesearch} \hfill Primary Author
\\
https://github.com/terabyte/stash-codesearch-plugin
\\
{\bf QBT - QBT Build Tool} \hfill Core Developer
\\
http://qbtbuildtool.com
\\

\section{INTERESTS} 
Open Source Software, Video Games, Poker, Skepticism, Classical Music, Scientific Pursuits.

\section{REFERENCES}
Available upon request

\end{resume}
\end{document}

%	%____________________________________________________________________________________
%	% Achievements
%	%    \section{\mysidestyle Achievements} 
%	%
%	%    \begin{list2} 
%	%    \item
%	%		Recognized as a leader in ownership and support of systems (Amazon and Palantir)
%	%    \item
%	%		Recognized for participation in recruiting regularly (Amazon and Palantir)
%	%    \item
%	%        Mentored interns and new-hires (Amazon and Palantir)
%	%    \item
%	%		Member of various school and community orchestras' cello section (Purdue Symphony Orchestra, Sammamish Symphony Orchestra, NovaVista Symphony Orchestra)
%	%    \end{list2}
%
%	%____________________________________________________________________________________
%	% Interests
%	\section{\mysidestyle Interests} 
%	Open Source Software, Video Games, Poker, Skepticism, Classical Music, Scientific Pursuits.
%
%	%____________________________________________________________________________________
%	% References
%	\section{\mysidestyle References}
%	{\sl References available upon request.}
%	%________________________________________________________________________________________
%\end{resume}
%\end{document}
%
%%________________________________________________________________________________________
%% EOF
%
